---
title: "Average Farm Size by Country"
author: "David Jackson"
date: "9/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(scales)
library(flextable)
library(dlookr)
```

## Our World In Data: Average Farm Size

* Source: https://ourworldindata.org/farm-size#average-farm-size-by-country

```{r}
farm_size <- read_csv("./average-farm-size.csv") %>% select(-Code) %>% rename(Country = Entity)
```
## Descriptive Stats Using dlookr

```{r}
farm_size %>% select(average_farm_size_ha) %>% dlookr::diagnose_numeric() %>% flextable()
```

## Begin Fun Stuff
### Less than One Hectare Arces for 2000

```{r}
farm_size %>% filter(average_farm_size_ha <=1 & Year ==2000) %>%
  
  ggplot() +
  geom_col(aes(x=average_farm_size_ha,y=Country)) +
  labs(title = "Countries with Farm Size Under 1 HA (2000)",
       x="Hectare Arces",y="Countries")

```

### Less than >1 and <=5 Hectare Arces for 2000

```{r}
farm_size %>% filter((average_farm_size_ha >1 & average_farm_size_ha <=5) & Year ==2000) %>%
  
  ggplot() +
  geom_col(aes(x=reorder(Country,average_farm_size_ha),y=average_farm_size_ha)) +
  labs(title = "Countries with Farm Size > 1 & <= 5 HA (2000)",
       y="Hectare Arces",x="Countries") + coord_flip()
```

### Less than >5 and <=10 Hectare Arces for 2000

```{r}
farm_size %>% filter((average_farm_size_ha >5 & average_farm_size_ha <=10) & Year ==2000) %>%
  
  ggplot() +
  geom_col(aes(x=reorder(Country,average_farm_size_ha),y=average_farm_size_ha)) +
  labs(title = "Countries with Farm Size > 5 & <= 10 HA (2000)",
       y="Hectare Arces",x="Countries") + coord_flip()
```

### Histogram of Farm Sizes In Hectare Arces

```{r}
farm_size %>% ggplot() + geom_histogram(aes(x=average_farm_size_ha)) +
  scale_x_log10() + labs(title = "Histogram by Farm Size in Hectare Arces",
                         x="Hectare Arces (log10)",y="Number of Farms")
```

