---
title: "Average Farm Size by Country"
author: "David Jackson"
date: "9/6/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,error = FALSE)
library(tidyverse)
library(dlookr)
library(scales)
library(flextable)
```

## Introduction

"Smallholders produce one-third of the world’s food, less than half of what many headlines claim"
 It is often claimed that smallholder farmers produce 70% or even 80% of the world’s food. This claim has even been made by the United Nations Food and Agriculture Organization (UN FAO).

## Into (Cont.)

"It has been a linchpin for agricultural and development policies. But it is wrong. Recent studies suggest that this figure is too high: smallholder farmers produce around one-third of the world’s food, less than half of what these headlines claim."

(Source: https://ourworldindata.org/farm-size#average-farm-size-by-country )


```{r}

farm_size <- read_csv("./average-farm-size.csv") %>% select(-Code) %>% rename(Country = Entity)

```

## Descriptive Stats For Farm Size

```{r}
farm_size %>% select(average_farm_size_ha) %>% dlookr::diagnose_numeric() %>% flextable()
```

## Histogram of Farm Size 

```{r}
farm_size %>% ggplot() + geom_histogram(aes(x=average_farm_size_ha)) +
  scale_x_log10() + labs(title = "Histogram by Farm Size in Hectare Arces",  x="Hectare Arces (Logarithmic scale(log10))",y="Number of Farms")
```

## Farms That Our  Less than One Hectare Arces (for 2000)

```{r}
farm_size %>% filter(average_farm_size_ha <=1 & Year ==2000) %>%
  
  ggplot() +
  geom_col(aes(x=average_farm_size_ha,y=Country)) +
  labs(title = "Countries with Farm Size Under 1 HA (2000)",
       x="Hectare Arces",y="Countries")

```

## Greater  than >1 and <=5 Hectare Arces (for 2000)

```{r}
farm_size %>% filter((average_farm_size_ha >1 & average_farm_size_ha <=5) & Year ==2000) %>%
  
  ggplot() +
  geom_col(aes(x=reorder(Country,average_farm_size_ha),y=average_farm_size_ha)) +
  labs(title = "Countries with Farm Size > 1 & <= 5 HA (2000)",
       y="Hectare Arces",x="Countries") + coord_flip()
```

##  Farms That Are Greater than >5 and <=10 Hectare Arces (for 2000)

```{r}
farm_size %>% filter((average_farm_size_ha >5 & average_farm_size_ha <=10) & Year ==2000) %>%
  
  ggplot() +
  geom_col(aes(x=reorder(Country,average_farm_size_ha),y=average_farm_size_ha)) +
  labs(title = "Countries with Farm Size > 5 & <= 10 HA (2000)",
       y="Hectare Arces",x="Countries") + coord_flip()
```